\documentclass[10pt]{article}
\usepackage[a4paper,margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}
\setlength{\parindent}{0pt}

% Formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[\hspace{0.3em}]
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
%\vspace{-.2ex} % Eliminates the small gap

\begin{document}

\begin{center}
  \textbf{\Large Jada Ebong} \\[0.2em]
  \href{mailto:jadaebong@gmail.com}{jadaebong@gmail.com} \quad | \quad (210) 286-1659 \\[0.2em]
  \href{https://github.com/JadaE}{github.com/JadaE} \quad | \quad \href{https://linkedin.com/in/jadaebong}{linkedin.com/in/jadaebong}
\end{center}

\section{Summary}
Jada Ebong has 5 years of experience as a creative Software Engineer specializing in backend systems, Python, and TypeScript. Seeking a developer role, she is passionate about writing clean and innovative code, growing ideas into reality, and curating a friendly user and team experience.

\section*{Education}
\textbf{University of Texas at San Antonio} \hfill B.S. Computer Science, 2020\\
Concentration in Software Engineering and Data Science

\section*{Skills}
\textbf{Certifications:} AWS Certified Cloud Practitioner (2023--2026) \quad
\textbf{Languages:} Python, React TypeScript, Java \quad
\textbf{Tools:} Agile/Scrum, Git, VSCode, Unity \\
\textbf{Soft:} Leadership, Communication, Team Building, Creative Thinker

\section*{Experience}
\textbf{JPMorgan Chase}, Houston, TX \\
\textit{Software Engineer II} \hfill 2023--Present
\begin{itemize}[leftmargin=*]
  \item Core backend developer of key algorithms for a firm-wide regulatory project with a strict deadline. 
  \item Developed automated data tools and controls using OOP Python and Pandas; paired with thorough unit tests.
  \item Built full-stack Python apps for Energy Commodity Traders who handle millions of dollars daily.
  \item Led API/data migration from vendor systems, saving hundreds of thousands annually.
  \item Routinely review and test senior-level code so production remains stable.
  
\end{itemize}
\textit{Software Engineer I} \hfill 2020--2023
\begin{itemize}[leftmargin=*]
  \item Developed React TypeScript web app for natural gas scheduling; improved accessibility and efficiency.
  \item Securely passed post-trade data and conducted 30+ production releases using Java, SpringBoot, and SQL.
  \item Graduated from JPMC's Software Engineer Program (SEP).
\end{itemize}

\textbf{BIF Technology}, San Antonio, TX \\
\textit{Software Engineer Intern} \hfill 2019--2020
\begin{itemize}[leftmargin=*]
  \item Built Java/SQL business intelligence software and company website.
  \item Supported sales efforts and served local communities as well as Puerto Rico on mission teams.
\end{itemize}

\section*{Leadership \& Volunteering}
%\textbf{Sacred Heart Clinic} \textit{Developer} \hfill 2024--Present\\
%Supporting internal systems and reducing manual labor for nonprofit medical staff.\\
\textbf{JPMC Leadership \& Engineering Advancement Program} \hfill 2024\\
Participated in a leadership program with 30 learning/speaking opportunities.
Pitched a documentation project, which was a former Hackathon 2nd place winner, to Houston leadership.\\
\textbf{SEP Committee} \textit{President} \hfill 2021--2022\\
Led a 15-person committee who organized 3--6 monthly events for 100+ new grads; created a community.\\
\textbf{UTSA ACM} \textit{Secretary} \hfill 2019--2020\\
Led Scrum and managed memberships for 100+ student members. Directed student experience for university Hackathon for 200+ attendees.

\section*{Projects}
\textbf{JaiDA} An AI chatbot using LangChain, LangGraph, Python, LaTex, and more on personal website hosted on GitHub Pages. Creates tailored resume per given job listing details.

\end{document}
